---
title: "VFSMOD with PWC Analysis"
author: "Your Name Here"
date: '2021-02-19'
output:
  html_notebook:
    code_folding: hide
  html_document:
    df_print: paged
---


```{r,echo=FALSE, results="hide", warning=FALSE, message=FALSE}
## YOU DO NOT NEED TO CHANGE ANYTHING IN THIS CODE BLOCK - YOU CAN HIDE IT BY CLICKING THE ARROW ON THE LEFT AT LINE 13
require(tidyr);require(dplyr);require(ggplot2);require(knitr); require(stringr)


getVFSDiff <- function(fldr, vfsWidth = 0.0, simYears = 50){
  fns <- dir(fldr, pattern = "Parent.txt", recursive = TRUE)
  concs <- do.call(rbind, lapply(fns, FUN = getConcsFromTxt, fldr = fldr, vfsWidth=vfsWidth, numRows = simYears))
  concs
}

getConcsFromTxt <- function(fn, fldr, vfsWidth, numRows){
  concs <- read.csv(paste( fldr, "/", fn[1], sep = ""), skip=19, nrows=numRows, header=FALSE, sep="")
  names(concs) <- c("Year","Peak","96-Hour","21-Day","60-Day","90-Day","365-Day","Benthic-Peak","Benthic-21-Day")
  concs$Run <- basename(fn[1])
  if (unlist(strsplit(concs$Run[1],"_"))[1] == "VFS"){
      concs$Type <- "VFS"
      if (vfsWidth != 0.0){
        concs$Type <- paste(vfsWidth, "m VFS", sep="")
      }
      concs$Active <- unlist(strsplit(concs$Run,"_"))[2]
  }
  else{
    concs$Type <- "No VFS"
    concs$Active <- unlist(strsplit(concs$Run,"_"))[1]
  }
 concs
}

`%notin%` <- Negate(`%in%`)
```


```{r}
pathToVVWMResults <- getwd()
vfsWidth <- 0.0
```


## Results

The following charts display the EECs with and without running VFSMOD for a single simulation.

```{r}
result <- getVFSDiff(pathToVVWMResults, vfsWidth = vfsWidth)
qplot(Year, Peak, data=result %>% select(Type, Year, Peak, Active), color=Type) + facet_wrap(~Active) + xlab("Simulation Year") + theme(axis.text.x = element_text(angle = 70, hjust = 1))
```

A Reduction Efficiency (RE) for a VFS can be defined as:

<center>$RE = 1-\frac{WithVFS}{WithoutVFS}\times100\%$</center>

such that the RE is 1 when the VFS prevents 100% of the pesticide from entering the water body that would enter without it. RE calculated using the yearly **peaks**:

```{r}
VFSDescription <- unique(result$Type)[2]

REPeak <- result %>% select(Year, Type, Peak, Active) %>% group_by(Active, Year) %>% spread(key = Type, value = Peak) %>% ungroup
REPeak$RE <- (1-(REPeak[[VFSDescription]]/REPeak$`No VFS`))*100

REYear <- result %>% select(Year, Type, `365-Day`, Active) %>% group_by(Active, Year) %>% spread(key = Type, value = `365-Day`) %>% ungroup
REYear$RE <- (1-REYear[[VFSDescription]]/REYear$`No VFS`)*100

qplot(Year, RE, data=REPeak %>% select(Year, RE, Active)) + facet_wrap(~Active) + xlab("Simulation Year") + ylab("Reduction Efficiency (%)") + theme(axis.text.x = element_text(angle = 70, hjust = 1)) + labs(title = paste("Reduction Efficiency of Peak EECs for", VFSDescription)) 
ggsave("PeakReductionEfficiency.PNG", width = 7, height = 4.25)
```

 RE calculated using the yearly **averages**:
 
```{r}
qplot(Year, RE, data=REYear %>% select(Year, RE, Active)) + facet_wrap(~Active) + xlab("Simulation Year") + ylab("Reduction Efficiency (%)") + theme(axis.text.x = element_text(angle = 70, hjust = 1)) + labs(title = paste("Reduction Efficiency of Yearly Averaged EECs for", VFSDescription)) 
ggsave("YearlyReductionEfficiency.PNG", width = 7, height = 4.25)
```
 
 